### 2014-02-25 paper/retrofit.tex
Proof checkpoint.

\subsection{Formal Guarantees}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
  We proof the lemma by induction on the derivation
  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
  could have been used to make the reduction step.
  \begin{description}
    \item[Case \textsc{I-done}] 
    \item[Case \textsc{I-noStep}] 
    \item[Case \textsc{I-fork}] 
    \item[Case \textsc{I-setLabel}]
  \end{description}
\end{proof}

>>>>

\clearpage % TODO: remove again, but keep for now to not have the text be split across 4 pages.
\subsection{Formal Guarantees}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:tsni}]
  \Red{It seems that the theorem, lemma as well as the proofs need to talk
    about |il| equivalence of |iS|, too, not just |il| equivalence of tasks.}

  We proof the lemma by induction on the derivation
  for~\eqref{eq:tsni-lemma-lhs}, and consider all possible rules that
  could have been used to make the reduction step.  In all cases, there
  needs to exist a task |it1| at the beginning of the list of |its1|.
  Consider two cases:
  \begin{itemize}
    \item $|erase il it1|=|bullet|$. In this case, we do not need to take a
    step for
    |its2|, because |its2'=its2| will already be |il|-equivalent to |its'|.
    In particular, note that 
    To see that, note that all existing tasks in |its1| are left in the
    same order and unmodified, except for |it1| (which has no
    corresponding task in |its2|, since it gets filtered).  The task |it1|
    gets dropped (by \textsc{I-noStep}), or
    transforms into a new task |it1'| as well as potentially spawning a new
    task |it1''|.  Since both |it1'| and |it1''| have a label that is
    at least as high as the label of |it1|, they will also get filtered.

    \alphacondition{We need all scheduling policies to not change the order
      of any tasks (except for the first one).  Newly spawned task can appear
      anywhere in the list.}
    \item $|erase il it1|\neq|bullet|$.  Here, there must be a corresponding
    task |it2|, such that $|it1|\approx_{|il|}|it2|$ (otherwise |its1| and
    |its2| could not be |il| equivalent).
    However, |it2| might not be at the beginning of the task list yet, but
    all tasks occurring before it must get erased by |erasef il|.
    In |its2|, we can first take some number of steps until |it2| moves
    to the front of the list (\Red{Say more precisely why
      (basically because we require the scheduling policy to do that)}).

    \alphacondition{The scheduling policy must eventually let any task in
      the task list evaluate.  In particular, it cannot get stuck when the
      first task gets stuck, or keep executing a small number of tasks
      exclusively forever (e.g. just execute the first task all the time
      if it gets into an infinite loop).}

    Therefore, after |its2| has potentially executed some number of steps
    to arrive at |its2''|, we are now in the situation where $|its1|\approx_{|il|}|its2''|$, and the first task |it1| and |it2| don't
    get erased and are |il| equivalent.  We consider all
    possible rules used to derive~\eqref{eq:tsni-lemma-lhs}:
    \begin{description}
      \item[Case \textsc{I-done}] 
      \item[Case \textsc{I-noStep}] 
      \item[Case \textsc{I-fork}] 
      \item[Case \textsc{I-setLabel}]
    \end{description}
  \end{itemize}
\end{proof}
